Model LF

### 2022-10-07 max_dp endogen stød.Rmd
Commit

COMMENT> lavet mhs til sensitivitets analyse
IDENTITY> max_gap
EQ> max_gap = 0.4
IF> sens2 <= 0
IDENTITY> max_gap
EQ> max_gap = 0.45
IF> sens2 > 0

@@

i_equip_nfc_k_ds_00 = S_model$simulation$i_equip_nfc_k_ds

@@

```{r}
###Gengivelse af stød til model
max_dp_bs2 = sens_2_bs$simulation$max_dp
wage_bs2 = sens_2_bs$simulation$wage
komp_r_bs2 = sens_2_bs$simulation$komp_r
part_bs2 = sens_2_bs$simulation$part
yk_ds_bs2 = sens_2_bs$simulation$yk_ds
pc_ds_bs2 = sens_2_bs$simulation$pc_ds
wage_ds_t_bs2 = sens_2_bs$simulation$wage_ds_t
pc_ds_bs2 = sens_2_bs$simulation$pc_ds
max_gap_bs2 = sens_2_bs$simulation$max_gap
wage_gap1_bs2 = sens_2_bs$simulation$wage_gap1

@@

```{r}
###Gengivelse af stød til model
max_dp_s2 = sens_2_S1$simulation$max_dp
wage_s2 = sens_2_S1$simulation$wage
komp_r_s2 = sens_2_S1$simulation$komp_r
part_s2 = sens_2_S1$simulation$part
yk_ds_s2 = sens_2_S1$simulation$yk_ds
pc_ds_s2 = sens_2_S1$simulation$pc_ds
wage_ds_t_s2 = sens_2_S1$simulation$wage_ds_t
pc_ds_s2 = sens_2_S1$simulation$pc_ds
max_gap_s2 = sens_2_S1$simulation$max_gap

wage_gap1_s2 = sens_2_S1$simulation$wage_gap1

```{r}
plot((wage_ds_t_s2/wage_ds_t_bs2), col= "red", ylim= c(0.9, 1.1));
lines((wage_ds_t_05/wage_ds_t_00), col="black");
legend("top", legend=c("No suppression",
                       "Wage growth"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

>>>>

COMMENT> lavet mhs til sensitivitets analyse
IDENTITY> max_gap
EQ> max_gap = 0.4
IF> sens2 <= 0
IDENTITY> max_gap
EQ> max_gap = 0.38
IF> sens2 > 0

@@

i_equip_nfc_k_ds_00 = S_model$simulation$i_equip_nfc_k_ds
inflation_00 = S_model$simulation$inflation

@@

```{r}
###Gengivelse af stød til model
max_dp_bs2 = sens_2_bs$simulation$max_dp
wage_bs2 = sens_2_bs$simulation$wage
komp_r_bs2 = sens_2_bs$simulation$komp_r
part_bs2 = sens_2_bs$simulation$part
yk_ds_bs2 = sens_2_bs$simulation$yk_ds
pc_ds_bs2 = sens_2_bs$simulation$pc_ds
wage_ds_t_bs2 = sens_2_bs$simulation$wage_ds_t
pc_ds_bs2 = sens_2_bs$simulation$pc_ds
max_gap_bs2 = sens_2_bs$simulation$max_gap
wage_gap1_bs2 = sens_2_bs$simulation$wage_gap1
inflation_bs2 = sens_2_bs$simulation$inflation
wage_ds_bs2 = sens_2_bs$simulation$wage_ds

@@

```{r}
###Gengivelse af stød til model
max_dp_s2 = sens_2_S1$simulation$max_dp
wage_s2 = sens_2_S1$simulation$wage
komp_r_s2 = sens_2_S1$simulation$komp_r
part_s2 = sens_2_S1$simulation$part
yk_ds_s2 = sens_2_S1$simulation$yk_ds
pc_ds_s2 = sens_2_S1$simulation$pc_ds
wage_ds_t_s2 = sens_2_S1$simulation$wage_ds_t
pc_ds_s2 = sens_2_S1$simulation$pc_ds
max_gap_s2 = sens_2_S1$simulation$max_gap
wage_ds_s2 = sens_2_S1$simulation$wage_ds
wage_gap1_s2 = sens_2_S1$simulation$wage_gap1
wage_gap_s2 = sens_2_S1$simulation$wage_gap

inflation_s2 = sens_2_S1$simulation$inflation
```

```{r}
plot((wage_ds_t_s2/wage_ds_t_00), col= "red", ylim= c(0.9, 1.1));
lines((wage_ds_t_05/wage_ds_t_00), col="black");
legend("top", legend=c("No suppression",
                       "Wage growth"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

```{r}
plot((inflation_s2-inflation_bs2), col= "red", ylim= c(-0.0004, 0.0035));
lines((inflation_05-inflation_00), col="black");
legend("top", legend=c("No suppression",
                       "Wage growth"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

```{r}
plot((wage_ds_s2/wage_ds_00), col= "red", ylim= c(0.995, 1.02));
lines((wage_ds_05/wage_ds_00), col="black");
legend("top", legend=c("No suppression",
                       "Wage growth"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```
